SMT-Based Generation of Symbolic Automata \thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-11-17 2017-Xudong-SMT/ActaInformatica.tex
Acta Inf. paper: Typo.
actions can have action subterms
corrected a couple of typos

\renewcommand{\P}{\mathcal V}
\def\Talg{\mathcal{T}_{\Sigma,\P}}
Formally, we assume the existence of a term algebra $\Talg$,
where $\Sigma$ is the signature of the data and action constructors,
and $\P$ a set of variables. Within $\Talg$, we distinguish a set of
data expressions $\mathcal{E}_\P$, including a set of Boolean
expressions $\mathcal{B}_{\P}$ ($\mathcal{B}_{\P}\subseteq\mathcal{E}_\P$).
On top of $\mathcal{E}_\P$ we build the action algebra
$\mathcal{A}_\P$, with $\mathcal{A}_\P\subseteq\mathcal{T}_\P$.
\QIN{As action expressions $\mathcal{A}_\P$ we built will not be used to present data terms, we have} 
$\mathcal{E}_\P\cap\mathcal{A}_\P=\emptyset$;
 action terms will use data expressions as sub-terms.
The function $\vars(t)$ identifies the set of variables in a term
$t\in\AlgT$.

@@

\ERIC{Each call to the SMT engine will return either SAT or UNSAT results, or may fail due to time bounds. Also, the accuracy of a `SAT' result may depend on the characteristics of the specific theory used to axiomatise the data domains and operators. Such theories may be intrinsically undecidable, or may not properly handled by the SMT engine (e.g. for recursive datatypes).
However, while building the open automaton, that is a symbolic representation of the pNet behavior, it is not logically incorrect to keep potentially unsatisfiable transitions, so we will treat undecidable results, and time bounds failures, as SAT. So the open automaton may have more transitions and states than the theoretical minimum.}

@@

\vspace{-5mm}
\begin{figure}[ht]
\centerline{ 
  \includegraphics[width=0.25\linewidth]{ActaXFIG/Enable1-aut}
  \hspace{25mm}
  \includegraphics[width=0.20\linewidth]{ActaXFIG/Enable2-aut}}
  \begin{minipage}{5.7cm}
$  \begin{array}{@{}r@{}l@{}}
    ot_1  = &\openrule{\{ \xrightarrow{a_1}_P \},\\ [\forall y_1. a_1\neq\delta(y_1)]}
    {A_0 \xrightarrow{a_1} A_0}\\
    ot_2  =& \openrule{
                            \{\xrightarrow{\delta(x_1)}_P,\,
                            \xrightarrow{acc(x_1)}_Q\}  }
    {A_0 \xrightarrow{\underline{\delta(x_1)}} A_1}\\
    ot_3  =& \openrule{
                          \{  \xrightarrow{a_2}_Q \},\\ [\forall y_2. a_2\neq acc(y_2)] }
    {A_1 \xrightarrow{a_2} A_1}
  \end{array}$
  \end{minipage}
  \hspace{2mm}
  \begin{minipage}{6cm}
$  \begin{array}{@{}r@{}l@{}}
    ot'_1  =& \openrule{
    	\{\xrightarrow{b_1}_P\}, ~~ [\forall y_1. b_1\neq\delta(y_1) \!\land\! v=0]}
    {B_0 \xrightarrow{b_1} B_0}\\
    ot'_2  =& \openrule{
                            \{\xrightarrow{\delta(x_2)}_P,\,
                            \xrightarrow{acc(x_2)}_Q \},~
                                        v=0,~
                                        \{v\gets 1\}}
    {B_0 \xrightarrow{\underline{\delta(x_2)}} B_1}\\
    ot'_3  =& \openrule{
                            \{\xrightarrow{b_2}_Q\}, ~~ [\forall y_2. b_2\neq acc(y_2) \!\land\! v=1] }
    {B_1 \xrightarrow{b_2} B_1}
  \end{array}$
  \end{minipage}
  \caption{The two open automata}
  \label{schema:enable-OAs}
\end{figure}

>>>>

\renewcommand{\P}{\mathcal V}
\def\Talg{\mathcal{T}_{\Sigma,\P}}
Formally, we assume the existence of a term algebra $\Talg$,
where $\Sigma$ is the signature of the data and action constructors,
and $\P$ a set of variables. Within $\Talg$, we distinguish a set of
data expressions $\mathcal{E}_\P$, including a set of Boolean
expressions $\mathcal{B}_{\P}$ ($\mathcal{B}_{\P}\subseteq\mathcal{E}_\P$).
On top of $\mathcal{E}_\P$ we build the action algebra
$\mathcal{A}_\P$, with $\mathcal{A}_\P\subseteq\mathcal{T}_\P$.
%% \QIN{As action expressions $\mathcal{A}_\P$ we built will not be used to present data terms, we have} 
%% $\mathcal{E}_\P\cap\mathcal{A}_\P=\emptyset$;
 \ERIC{Action terms can use both data and action expressions as sub-terms}.
The function $\vars(t)$ identifies the set of variables in a term
$t\in\AlgT$.

@@

\ERIC{Each call to the SMT engine will return either SAT or UNSAT results, or may fail due to time bounds. Also, the accuracy of a `SAT' result may depend on the characteristics of the specific theory used to axiomatise the data domains and operators. Such theories may be intrinsically undecidable, or may not  be properly handled by the SMT engine (e.g. for recursive datatypes).
However, while building the open automaton, which is a symbolic representation of the pNet behavior, it is not logically incorrect to keep potentially unsatisfiable transitions, so we will treat undecidable results, and time bounds failures, as SAT. So the open automaton may have more transitions and states than the theoretical minimum.}

@@

\vspace{-5mm}
\begin{figure}[ht]
\centerline{ 
  \includegraphics[width=0.25\linewidth]{ActaXFIG/Enable1-aut}
  \hspace{25mm}
  \includegraphics[width=0.20\linewidth]{ActaXFIG/Enable2-aut}}
  \begin{minipage}{5.7cm}
$  \begin{array}{@{}r@{}l@{}}
    ot_1  = &\openrule{\{ \xrightarrow{a_1}_P \},\\ [\forall y_1. a_1\neq\delta(y_1)]}
    {A_0 \xrightarrow{a_1} A_0}\\
    ot_2  =& \openrule{
                            \{\xrightarrow{\delta(x_1)}_P,\,
                            \xrightarrow{acc(x_1)}_Q\}  }
    {A_0 \xrightarrow{\underline{\delta(x_1)}} A_1}\\
    ot_3  =& \openrule{
                          \{  \xrightarrow{a_2}_Q \},\\ [\forall y_2. a_2\neq acc(y_2)] }
    {A_1 \xrightarrow{a_2} A_1}
  \end{array}$
  \end{minipage}
  \hspace{2mm}
  \begin{minipage}{6cm}
$  \begin{array}{@{}r@{}l@{}}
    ot'_1  =& \openrule{
    	\{\xrightarrow{b_1}_P\}, ~~ [\forall y_1. b_1\neq\delta(y_1) \!\land\! v=0]}
    {B_0 \xrightarrow{b_1} B_0}\\
    ot'_2  =& \openrule{
                            \{\xrightarrow{\delta(x_2)}_P,\,
                            \xrightarrow{acc(x_2)}_Q \},~
                                        [v=0],~
                                        \{v\gets 1\}}
    {B_0 \xrightarrow{\underline{\delta(x_2)}} B_1}\\
    ot'_3  =& \openrule{
                            \{\xrightarrow{b_2}_Q\}, ~~ [\forall y_2. b_2\neq acc(y_2) \!\land\! v=1] }
    {B_1 \xrightarrow{b_2} B_1}
  \end{array}$
  \end{minipage}
  \caption{The two open automata}
  \label{schema:enable-OAs}
\end{figure}
